\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-23 syntax.tex
Answer questions.
question
unanswered questions

\begin{figure}[!htb]
  \begin{alignat*}{3}
    \text{Inductive Type Signature}   \quad & \tau       &&= w\cdot~|~w^+~\tau~A~B~|~\tau[\gamma] \\
    \text{Linkage Signature}          \quad & \sigma       &&= \nu\cdot~|~\nu^+~\sigma~\{f\}~T~|~\sigma[\gamma]~|~p_1\nu~\sigma~|~"RecSig"~\tau~T \\
    \text{Seal}          \quad & f       &&= t~|~p_f\nu~\sigma\\    
    \text{Types}   \quad & A, B, T        &&= ...~|~\bW \tau~|~\pi_1^j~|~\pi_2^j~|~\cL\sigma~|~\cC\sigma~|~p_1\nu'~\sigma~|~p_2\nu~\sigma~|~"RecSig1"~A~B~T~|\\
    \text{Terms}   \quad & t, t_1, t_2    &&= ...~|~"W"~T~|~"Wsup"~T~t_1~t_2~|~\mu\cdot~|~\mu^+~t~\{f\}~T~|~p_1\mu~t~|~p_2\mu~t~|~\cCt~t~|\\ & &&"prjR"~j~o~|~"Wrec"~t_1~t_2~|~"inh"~h~t\\
    \text{Inheritance Structure} \quad & h, h' &&= "inhid"~|~"inhov"~h~t~|~"inhext"~h~t~|~"inhinh"~h~|~"inh"~h~|~"inhnest"~h~h'
  \end{alignat*}
\caption{Overview of Instrinsically-typed Syntax for extended MLTT}
\end{figure}
\begin{figure}[!htb]
  \begin{align*}
&\sigma~:~"Sig"~\Gamma~n&&\mathboxtext{\goodSig{\Gamma}{\sigma}{n}}  &&\tau~:~"WSig"~\Gamma~n&&\mathboxtext{\goodWSig{\Gamma}{\tau}{n}} \\ &h~:~"Inh"~\Gamma~\sigma_1~\sigma_2&&\mathboxtext{\goodInh{\Gamma}{h}{\sigma}{\tau}} && f~:~"Seal"~\Gamma~\sigma~T&&\mathboxtext{\goodSeal{\Gamma}{f}{\sigma}{A}}
  \end{align*}
\caption{Extended Judgement forms, as Agda types}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Sig]
      {\goodCtx{\Gamma}{i} \quad n \in \nat}
      {\goodSig{\Gamma}{\_}{n} \text{ is well-formed}}
      $$
      $$
      \Rule[name=Seal]
      {\goodCtx{\Gamma}{i} \quad \goodSig{\Gamma}{\sigma}{n} 
      \quad \goodType{\Gamma}{A}{} }
      {\goodSeal{\Gamma}{\_}{\sigma}{A} \text{ is well-formed}}
      $$\YZ{Doesn't the left column show well-formedness rules for ONLY TWO of the four new judgments? Besides, are these rules used anywhere in the following? Seems a bit unusual to have well-formedness rules for judgments per se.}\EDJreply{Yes. Right column show all the well-formedness rule for all the judgement. That is unusual because it is a direct translation from QIIT. }
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Sig  : Con → ℕ → Set
      data WSig : Con → ℕ → Set 
      data Inh  : (Γ : Con) → Sig Γ n → Sig Γ m → Set
      Seal : (Γ : Con) → Sig Γ n → Sig Γ n → Set
    \end{minted}
  \end{minipage}

@@

$$
\Rule[name=Ind-Type]
{\goodTerm{\Gamma}{T}{\bW \tau}}
{\goodTerm{\Gamma}{"W" \ T}{\cU}
}
\quad 
\Rule[]{}{\goodTerm{\Gamma}{\star}{\bW \tau}}\YZ{What is star? Is it just tau?}
\quad
\Rule[name=Ind-Term]
{\goodTerm{\Gamma}{T}{\bW \tau}
  \quad \goodTerm{\Gamma}{a}{\pi^j_1\tau}
  \quad \goodTerm{\Gamma, \pi^j_2\tau[(id, a)]}{b}{El~("W"~T)}}
{\goodTerm{\Gamma}{"Wsup"~T~a~b}{El~("W"~T)} }
$$

@@

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\tau}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\tau~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\tau~R)}
\quad j < N
}
{\goodTerm{\Gamma}{"prjR"~j~o}{("RecSig1"~(\pi_1^j \tau)~(\pi_2^j \tau)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{T}{\bW \tau}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\tau~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}
$$

@@

$$
\Rule[name=Inh-Ext]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
  \quad \goodTerm{\Gamma, A_2}{t}{T}}
{\goodInh{\Gamma}{"inhext" \ h \ t}{\sigma_1}{(\nu^+ \  \sigma_2\  T)}}
\quad
\Rule[name=Inh-Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodType{\Gamma, A_1}{T}{}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
}
{\goodInh{\Gamma}{"inhinh" \ h}{(\nu^+ \  \sigma_1 \  T)}{(\nu^+ \  \sigma_2 \  T[(\pi_1, \uparrow^s)])}}\YZ{Should the term be 'inhinh h t' instead of 'inhinh h', where t is the field being inherited?}
$$
$$
\Rule[name=Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma}{l}{\cL \sigma_1}
}
{\goodTerm{\Gamma}{("inh" \ h \ l)}{\cL \sigma_2}} 
\quad
\Rule[name=Inh+Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
\\\\
\goodInh{\Gamma, A_2}{i}{\tau_1[(\pi_1, \uparrow^s)]}{\tau_2}}
{\goodInh{\Gamma}{"inhnest" \ h \ i}{(\nu^+ \  \sigma_1\  \cL\tau_1)}{(\nu^+ \  \sigma_2\  \cL\tau_2)}}
\quad
$$

>>>>

\begin{figure}[!htb]
  \begin{alignat*}{3}
    \text{Inductive Type Signature}   \quad & \tau       &&= w\cdot~|~w^+~\tau~A~B~|~\tau[\gamma] \\
    \text{Linkage Signature}          \quad & \sigma       &&= \nu\cdot~|~\nu^+~\sigma~\{f\}~T~|~\sigma[\gamma]~|~p_1\nu~\sigma~|~"RecSig"~\tau~T \\
    \text{Seal}          \quad & f       &&= t~|~p_f\nu~\sigma\\    
    \text{Types}   \quad & A, B, T        &&= ...~|~\bW \tau~|~\pi_1^j~|~\pi_2^j~|~\cL\sigma~|~\cC\sigma~|~p_1\nu'~\sigma~|~p_2\nu~\sigma~|~"RecSig1"~A~B~T~|\\
    \text{Terms}   \quad & t, t_1, t_2    &&= ...~|~"W"~T~|~"Wsup"~T~t_1~t_2~|~\mu\cdot~|~\mu^+~t~\{f\}~T~|~p_1\mu~t~|~p_2\mu~t~|~\cCt~t~|\\ & &&"prjR"~j~o~|~"Wrec"~t_1~t_2~|~"inh"~h~t\\
    \text{Inheritance Structure} \quad & h, h' &&= "inhid"~|~"inhov"~h~t~|~"inhext"~h~t~|~"inhinh"~h~|~"inh"~h~|~"inhnest"~h~h'
  \end{alignat*}\YZ{ What is 'W T'? Do you mean 'c T'?  }\YZreply{Why is Seal not merged into Terms?}
\caption{Overview of Instrinsically-typed Syntax for extended MLTT}
\end{figure}
\begin{figure}[!htb]
  \begin{align*}
&\sigma~:~"Sig"~\Gamma~n&&\mathboxtext{\goodSig{\Gamma}{\sigma}{n}}  &&\tau~:~"WSig"~\Gamma~n&&\mathboxtext{\goodWSig{\Gamma}{\tau}{n}} \\ &h~:~"Inh"~\Gamma~\sigma_1~\sigma_2&&\mathboxtext{\goodInh{\Gamma}{h}{\sigma}{\tau}} && f~:~"Seal"~\Gamma~\sigma~T&&\mathboxtext{\goodSeal{\Gamma}{f}{\sigma}{A}}
  \end{align*}
\caption{Extended Judgement forms, as Agda types}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Sig]
      {\goodCtx{\Gamma}{i} \quad n \in \nat}
      {\goodSig{\Gamma}{\_}{n} \text{ is well-formed}}
      $$
      $$
      \Rule[name=Seal]
      {\goodCtx{\Gamma}{i} \quad \goodSig{\Gamma}{\sigma}{n} 
      \quad \goodType{\Gamma}{A}{} }
      {\goodSeal{\Gamma}{\_}{\sigma}{A} \text{ is well-formed}}
      $$\YZ{Doesn't the left column show well-formedness rules for ONLY TWO of the four new judgments? Besides, are these rules used anywhere in the following? Seems a bit unusual to have well-formedness rules for judgments per se.}\EDJreply{Yes. Right column show all the well-formedness rule for all the judgement. That is unusual because it is a direct translation from QIIT. }
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Sig  : Con → ℕ → Set
      data WSig : Con → ℕ → Set 
      data Inh  : (Γ : Con) → Sig Γ n → Sig Γ m → Set
      Seal : (Γ : Con) → Sig Γ n → Sig Γ n → Set
    \end{minted}
  \end{minipage}

@@

$$
\Rule[name=Ind-Type]
{\goodTerm{\Gamma}{T}{\bW \tau}}
{\goodTerm{\Gamma}{"W" \ T}{\cU}
}
\quad 
\Rule[]{}{\goodTerm{\Gamma}{\star}{\bW \tau}}\YZ{What is star? Is it just tau??}
\quad
\Rule[name=Ind-Term]
{\goodTerm{\Gamma}{T}{\bW \tau}
  \quad \goodTerm{\Gamma}{a}{\pi^j_1\tau}
  \quad \goodTerm{\Gamma, \pi^j_2\tau[(id, a)]}{b}{El~("W"~T)}}
{\goodTerm{\Gamma}{"Wsup"~T~a~b}{El~("W"~T)} }
$$

@@

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\tau}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\tau~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\tau~R)}
\quad j < N
}
{\goodTerm{\Gamma}{"prjR"~j~o}{("RecSig1"~(\pi_1^j \tau)~(\pi_2^j \tau)~R)}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{T}{\bW \tau}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\tau~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}
$$

@@

$$
\Rule[name=Inh-Ext]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
  \quad \goodTerm{\Gamma, A_2}{t}{T}}
{\goodInh{\Gamma}{"inhext" \ h \ t}{\sigma_1}{(\nu^+ \  \sigma_2\  T)}}
\quad
\Rule[name=Inh-Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodType{\Gamma, A_1}{T}{}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
}
{\goodInh{\Gamma}{"inhinh" \ h}{(\nu^+ \  \sigma_1 \  T)}{(\nu^+ \  \sigma_2 \  T[(\pi_1, \uparrow^s)])}}\YZ{Should the term be 'inhinh h t' instead of 'inhinh h', where t is the field being inherited??}
$$
$$
\Rule[name=Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma}{l}{\cL \sigma_1}
}
{\goodTerm{\Gamma}{("inh" \ h \ l)}{\cL \sigma_2}} 
\quad
\Rule[name=Inh+Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
\\\\
\goodInh{\Gamma, A_2}{i}{\tau_1[(\pi_1, \uparrow^s)]}{\tau_2}}
{\goodInh{\Gamma}{"inhnest" \ h \ i}{(\nu^+ \  \sigma_1\  \cL\tau_1)}{(\nu^+ \  \sigma_2\  \cL\tau_2)}}
\quad
$$
